---
title: "Overall insight into the accuracy of one’s truth judgments"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 3
editor_options:
  chunk_output_type: console
---



# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = TRUE,
	cache = FALSE
)

```



# Source `dependencies.R`

```{r dependencies, message=FALSE, code=readr::read_lines(here::here("code/_dependencies.R"))}
source(here::here("code/_dependencies.R"))

```



# Load data

```{r load_data}
metad_group_all_participants_mcmc <- read_rds(here::here("output/models/group/metad_group_all_participants_mcmc.rds"))

metad_group <- read_rds(here::here("output/models/group/metad_group.rds"))

metad_group_all_participants <- metad_group %>% 
  filter(name == "all participants")

```



# H1.1 / H1.2: Metacognitive ideal hypothesis / Domain comparison hypothesis
H1.1: Metacognitive efficiency for political statements is lower than the
theoretically optimal metacognitive efficiency of Mratio = 1
(see p.5 of preregistration:
https://osf.io/veja6/files/osfstorage/614c91e915e9a4005d9239cf).

H1.2: Metacognitive efficiency for political statements is lower than for
non-politicized domains such as biology and physics (Mratio = 0.99; Fischer et al.,
2019) (see p.5 of preregistration:
https://osf.io/veja6/files/osfstorage/614c91e915e9a4005d9239cf).

```{r overall_insight}
# compare 95% CI and ROPE (i.e., 0.9 - 1.1)
mratio <- metad_group_all_participants_mcmc[[1]] %>%
  filter(Parameter == "mu_logMratio") %>%
  mutate(exp_value = exp(value))

below_rope <- rope(mratio$exp_value, c(-100 , 0.9), ci = 1)
below_rope <- below_rope$ROPE_Percentage * 100

within_rope <- rope(mratio$exp_value, c(0.9, 1.1), ci = 1)
within_rope <- within_rope$ROPE_Percentage * 100

above_rope <- rope(mratio$exp_value, c(1.1, 100), ci = 1)
above_rope <- above_rope$ROPE_Percentage * 100

# plot trace mcmc
traceplot(metad_group_all_participants_mcmc[[4]])

# figure posterior distribution of Mratio for all participants
fig_mcmc <- metad_group_all_participants_mcmc[[1]] %>%
  filter(Parameter == "mu_logMratio") %>%
  ggplot(aes(exp(value))) +
  geom_histogram(
    binwidth = 0.005,
    fill = "blue",
    colour = "grey",
    alpha = 0.5
  ) +
  geom_vline(xintercept = metad_group_all_participants$Mratio_g,
             linetype = "dashed",
             size = 1.5) +
  geom_vline(
    xintercept = 1,
    colour = "black",
    linetype = "solid",
    size = 1.5
  ) +
  geom_segment(
    aes(
      x = metad_group_all_participants$Mratio_g.lower,
      y = 50,
      xend = metad_group_all_participants$Mratio_g.upper,
      yend = 50
    ),
    colour = "grey",
    size = 2.5
  ) +
  ylab("Sample count") +
  xlab(expression(italic("Mratio"))) +
  theme_minimal_hgrid()
fig_mcmc

save_plot(
  here("output/figures/fig_mcmc.pdf"),
  fig_mcmc,
  base_width = 12,
  base_height = 6.5
)

```

The posterior distribution is `r below_rope`% below the low limit of the ROPE,
`r within_rope`% within the ROPE, and `r above_rope`% above the high limit of the ROPE.
