---
title: "Predictors of metacognitive efficiency"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 3
editor_options:
  chunk_output_type: console
---



# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = TRUE,
	cache = FALSE
)

```



# Source `dependencies.R`

```{r dependencies, message=FALSE, code=readr::read_lines(here::here("code/_dependencies.R"))}
source(here::here("code/_dependencies.R"))

```



# Load data

```{r load_data}
# load files
participants <- read_rds(here::here("output/participants.rds"))
metad_indiv_all_participants_meta_d_cleaned <-
  read_rds(
    here::here(
      "output/models/indiv/metad_cleaned/metad_indiv_all_participants_meta_d_cleaned.rds"
    )
  )
metad_indiv_all_participants_m_ratio_cleaned <-
  read_rds(
    here::here(
      "output/models/indiv/mratio_cleaned/metad_indiv_all_participants_m_ratio_cleaned.rds"
    )
  )
metad_indiv_all_participants_m_diff_cleaned <-
  read_rds(
    here::here(
      "output/models/indiv/mdiff_cleaned/metad_indiv_all_participants_m_diff_cleaned.rds"
    )
  )

# merge to `dat`
dat <- participants %>%
  left_join(metad_indiv_all_participants_meta_d_cleaned %>%
              select(id, d1, meta_d),
            by = "id") %>%
  left_join(metad_indiv_all_participants_m_ratio_cleaned %>%
              select(id, m_ratio),
            by = "id") %>%
  left_join(metad_indiv_all_participants_m_diff_cleaned %>%
              select(id, m_diff),
            by = "id")  
dat

# write to disk
write_rds(dat, here("output/dat.rds"), compress = "gz")
write_csv(dat, here("output/dat.csv"))

```



# H3.1: Faith in intuition for facts hypothesis
Hypothesis: The higher citizens’ “Faith in Intuition for Facts”, the lower their
metacognitive efficiency for political statements
(see p.8 of preregistration:
https://osf.io/veja6/files/osfstorage/614c91e915e9a4005d9239cf).

Test: We plot each participant’s point prediction for Mratio (Mdiff)
against their faith in intuition for facts using robust LOESS smooths and 95%
confidence bands. Then, we also run a Spearman correlation.

## d'

```{r faith_intuition_d1}
# plot robust smooth
fig_faith_intuition_d1 <- dat %>%
  ggplot(aes(x = faith_intuition,
             y = d1)) +
  xlim(1, 5) +
  xlab("Faith in intuition for facts") +
  ylab("d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_faith_intuition_d1 <-
  ggMarginal(fig_faith_intuition_d1, type = "histogram")

fig_faith_intuition_d1

# compute correlation
cor.test(dat$faith_intuition, dat$d1, method = c("spearman"))

```

## meta-d'

```{r faith_intution_meta_d}
fig_faith_intuition_meta_d <- dat %>%
  ggplot(aes(x = faith_intuition,
             y = meta_d)) +
  xlim(1, 5) +
  xlab("Faith in intuition for facts") +
  ylab("meta-d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_faith_intuition_meta_d <-
  ggMarginal(fig_faith_intuition_meta_d, type = "histogram")

fig_faith_intuition_meta_d

# compute correlation
cor.test(dat$faith_intuition, dat$meta_d, method = c("spearman"))

```

## Mratio

```{r faith_intuition_mratio}
# plot robust smooth
fig_faith_intuition_mratio <- dat %>%
  ggplot(aes(x = faith_intuition,
             y = m_ratio)) +
  xlim(1, 5) +
  xlab("Faith in intuition for facts") +
  ylab("Mratio") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_faith_intuition_mratio <-
  ggMarginal(fig_faith_intuition_mratio, type = "histogram")

fig_faith_intuition_mratio

# compute correlation
cor.test(dat$faith_intuition, dat$m_ratio, method = c("spearman"))

```

## Mdiff

```{r faith_intuition_mdiff}
# plot robust smooth
fig_faith_intuition_mdiff <- dat %>%
  ggplot(aes(x = faith_intuition,
             y = m_diff)) +
  xlim(1, 5) +
  xlab("Faith in intuition for facts") +
  ylab("Mdiff") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_faith_intuition_mdiff <-
  ggMarginal(fig_faith_intuition_mdiff, type = "histogram")

fig_faith_intuition_mdiff

cor.test(dat$faith_intuition, dat$m_diff, method = c("spearman"))

```



# H3.2: Truth is political hypothesis
Hypothesis: The higher citizens’ belief that “Truth is Political”, the lower their
metacognitive efficiency for political statements
(see p.8 of preregistration:
https://osf.io/veja6/files/osfstorage/614c91e915e9a4005d9239cf).

Test: We plot each participant’s point prediction for Mratio (Mdiff) against
their beliefs that truth is political using robust LOESS smooths and 95% confidence
bands. Then, we also run a Spearman correlation.





## d'

```{r truth_political_d1}
# plot robust smooth
fig_truth_political_d1 <- dat %>%
  ggplot(aes(x = truth_political,
             y = d1)) +
  xlim(1, 5) +
  xlab("Truth is political") +
  ylab("d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_truth_political_d1 <-
  ggMarginal(fig_truth_political_d1, type = "histogram")

fig_truth_political_d1

# compute correlation
cor.test(dat$truth_political, dat$d1, method = c("spearman"))

```

## meta-d'

```{r truth_political_meta_d}
fig_truth_political_meta_d <- dat %>%
  ggplot(aes(x = truth_political,
             y = meta_d)) +
  xlim(1, 5) +
  xlab("Truth is political") +
  ylab("meta-d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_truth_political_meta_d <-
  ggMarginal(fig_truth_political_meta_d, type = "histogram")

fig_truth_political_meta_d

# compute correlation
cor.test(dat$truth_political, dat$meta_d, method = c("spearman"))

```

## Mratio

```{r truth_political_mratio}
# plot robust smooth
fig_truth_political_mratio <- dat %>%
  ggplot(aes(x = truth_political,
             y = m_ratio)) +
  xlim(1, 5) +
  xlab("Truth is political") +
  ylab("Mratio") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_truth_political_mratio <-
  ggMarginal(fig_truth_political_mratio, type = "histogram")

fig_truth_political_mratio

# compute correlation
cor.test(dat$truth_political, dat$m_ratio, method = c("spearman"))

```

## Mdiff

```{r truth_political_mdiff}
# plot robust smooth
fig_truth_political_mdiff <- dat %>%
  ggplot(aes(x = truth_political,
             y = m_diff)) +
  xlim(1, 5) +
  xlab("Truth is political") +
  ylab("Mdiff") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_truth_political_mdiff <-
  ggMarginal(fig_truth_political_mdiff, type = "histogram")

fig_truth_political_mdiff

cor.test(dat$truth_political, dat$m_diff, method = c("spearman"))

```



# H3.3: Need for evidence hypothesis
Hypothesis: The higher citizens’ “Need for Evidence”, the higher their metacognitive
efficiency for political statements
(see p.8 of preregistration:
https://osf.io/veja6/files/osfstorage/614c91e915e9a4005d9239cf).

Test: We plot each participant’s point prediction for Mratio (Mdiff) against
their need for evidence using robust LOESS smooths and 95% confidence
bands. Then, we also run a Spearman correlation.

## d'

```{r need_evidence_d1}
# plot robust smooth
fig_need_evidence_d1 <- dat %>%
  ggplot(aes(x = need_evidence,
             y = d1)) +
  xlim(1, 5) +
  xlab("Need for evidence") +
  ylab("d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_need_evidence_d1 <-
  ggMarginal(fig_need_evidence_d1, type = "histogram")

fig_need_evidence_d1

# compute correlation
cor.test(dat$need_evidence, dat$d1, method = c("spearman"))

```

## meta-d'

```{r need_evidence_meta_d}
fig_need_evidence_meta_d <- dat %>%
  ggplot(aes(x = need_evidence,
             y = meta_d)) +
  xlim(1, 5) +
  xlab("Need for evidence") +
  ylab("meta-d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_need_evidence_meta_d <-
  ggMarginal(fig_need_evidence_meta_d, type = "histogram")

fig_need_evidence_meta_d

# compute correlation
cor.test(dat$need_evidence, dat$meta_d, method = c("spearman"))

```

## Mratio

```{r need_evidence_mratio}
# plot robust smooth
fig_need_evidence_mratio <- dat %>%
  ggplot(aes(x = need_evidence,
             y = m_ratio)) +
  xlim(1, 5) +
  xlab("Need for evidence") +
  ylab("Mratio") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_need_evidence_mratio <-
  ggMarginal(fig_need_evidence_mratio, type = "histogram")

fig_need_evidence_mratio

# compute correlation
cor.test(dat$need_evidence, dat$m_ratio, method = c("spearman"))

```

## Mdiff

```{r need_evidence_mdiff}
# plot robust smooth
fig_need_evidence_mdiff <- dat %>%
  ggplot(aes(x = need_evidence,
             y = m_diff)) +
  xlim(1, 5) +
  xlab("Need for evidence") +
  ylab("Mdiff") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_need_evidence_mdiff <-
  ggMarginal(fig_need_evidence_mdiff, type = "histogram")

fig_need_evidence_mdiff

cor.test(dat$need_evidence, dat$m_ratio, method = c("spearman"))

```



# H3.4: Age hypothesis
Hypothesis: Metacognitive efficiency for political statements declines with age
(see p.8 of preregistration:
https://osf.io/veja6/files/osfstorage/614c91e915e9a4005d9239cf).

Test: We plot each participant’s point prediction for Mratio (Mdiff) against
their age using robust LOESS smooths and 95% confidence bands. Then, we also run
a Spearman correlation.

## d'

```{r age_d1}
# plot robust smooth
fig_age_d1 <- dat %>%
  ggplot(aes(x = age,
             y = d1)) +
  xlab("Age") +
  ylab("d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_age_d1 <-
  ggMarginal(fig_age_d1, type = "histogram")

fig_age_d1

# compute correlation
cor.test(dat$age, dat$d1, method = c("spearman"))

```

## meta-d'

```{r age_meta_d}
fig_age_meta_d <- dat %>%
  ggplot(aes(x = age,
             y = meta_d)) +
  xlab("Age") +
  ylab("meta-d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_age_meta_d <-
  ggMarginal(fig_age_meta_d, type = "histogram")

fig_age_meta_d

# compute correlation
cor.test(dat$age, dat$meta_d, method = c("spearman"))

```

## Mratio

```{r age_mratio}
# plot robust smooth
fig_age_mratio <- dat %>%
  ggplot(aes(x = age,
             y = m_ratio)) +
  xlab("Age") +
  ylab("Mratio") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_age_mratio <- ggMarginal(fig_age_mratio, type = "histogram")

fig_age_mratio

# compute correlation
cor.test(dat$age, dat$m_ratio, method = c("spearman"))

```

## Mdiff

```{r age_mdiff}
# plot robust smooth
fig_age_mdiff <- dat %>%
  ggplot(aes(x = age,
             y = m_diff)) +
  xlab("Age") +
  ylab("Mdiff") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_age_mdiff <- ggMarginal(fig_age_mdiff, type = "histogram")

fig_age_mdiff

cor.test(dat$age, dat$m_diff, method = c("spearman"))

```

# H3.1-3.4: Plot all predictors in one figure

```{r psych_factors_age_merged}
# Mratio
fig_epistemic_age_mratio_merged <- ggarrange(
  fig_faith_intuition_mratio,
  fig_truth_political_mratio,
  fig_need_evidence_mratio,
  fig_age_mratio,
  ncol = 2,
  nrow = 2,
  labels = c("A", "B", "C", "D")
)
fig_epistemic_age_mratio_merged

# Mdiff
fig_epistemic_age_mdiff_merged <- ggarrange(
  fig_faith_intuition_mdiff,
  fig_truth_political_mdiff,
  fig_need_evidence_mdiff,
  fig_age_mdiff,
  ncol = 2,
  nrow = 2,
  labels = c("A", "B", "C", "D")
)
fig_epistemic_age_mdiff_merged

save_plot(
  here("output/figures/fig_epistemic_age_mdiff_merged.pdf"),
  fig_epistemic_age_mdiff_merged,
  base_width = 10,
  base_height = 10
)

```



# Additional: Education
Hypothesis: Metacognitive efficiency for political statements increases with education.

Test: We plot each participant’s point prediction for Mratio (Mdiff) against
their age using robust LOESS smooths and 95% confidence bands. Then, we also run
a Spearman correlation.

## d'

```{r educ_d1}
# plot robust smooth
fig_educ_d1 <- dat %>%
  ggplot(aes(x = educ,
             y = d1)) +
  xlab("Education") +
  ylab("d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_educ_d1 <-
  ggMarginal(fig_educ_d1, type = "histogram")

fig_educ_d1

# compute correlation
cor.test(dat$educ, dat$d1, method = c("spearman"))

```

## meta-d'

```{r educ_meta_d}
fig_educ_meta_d <- dat %>%
  ggplot(aes(x = educ,
             y = meta_d)) +
  xlab("Education") +
  ylab("meta-d'") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_educ_meta_d <-
  ggMarginal(fig_educ_meta_d, type = "histogram")

fig_educ_meta_d

# compute correlation
cor.test(dat$educ, dat$meta_d, method = c("spearman"))

```

## Mratio

```{r educ_mratio}
# plot robust smooth
fig_educ_mratio <- dat %>%
  ggplot(aes(x = educ,
             y = m_ratio)) +
  xlab("Education") +
  ylab("Mratio") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_educ_mratio <-
  ggMarginal(fig_educ_mratio, type = "histogram")

fig_educ_mratio

# compute correlation
cor.test(dat$educ, dat$m_ratio, method = c("spearman"))

```

## Mdiff

```{r educ_mdiff}
# plot robust smooth
fig_educ_mdiff <- dat %>%
  ggplot(aes(x = educ,
             y = m_diff)) +
  xlab("Education") +
  ylab("Mdiff") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  geom_point(alpha = .5) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

fig_educ_mdiff <-
  ggMarginal(fig_educ_mdiff, type = "histogram")

fig_educ_mdiff

cor.test(dat$educ, dat$m_diff, method = c("spearman"))

```
