---
title: "Make data"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 3
editor_options:
  chunk_output_type: console
---



# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = TRUE,
  cache = FALSE
)

```



# Source `dependencies.R`

```{r dependencies, message=FALSE, code=readr::read_lines(here::here("code/_dependencies.R"))}
source(here::here("code/_dependencies.R"))

```



# Load data

## Panel data

```{r load_panel_data}
# download panel data
if (!file.exists(here("data", "panelPublic.tab"))) {
  download_file(url = "https://dataverse.harvard.edu/api/access/datafile/4461145",
                output = here("data", "panelPublic.tab"))
}

# load panel data
raw <- read_tsv(here("data/panelPublic.tab")) %>%
  mutate(id = row_number()) 

raw_n_initial <- nrow(raw)

raw

```

We start out with `r raw_n_initial` participants.

## Statement slant and satire data

```{r load_statement_slant_and_satire_data}
# download statement slant data
if (!file.exists(here("data", "AMTstatementSlant.tab"))) {
  download_file(url = "https://dataverse.harvard.edu/api/access/datafile/4461138",
                output = here("data", "AMTstatementSlant.tab"))
}

# load statement slant data
statements_slant <- read_tsv(here("data/AMTstatementSlant.tab")) %>%
  separate(statement_num, c("statement", "wave"), "e_W") %>%
  mutate(wave = as.integer(wave))

# load statement satire data
statements_satire <-
  read_delim(
    here("data/statements_URLs_satire.csv"),
    delim = ";",
    escape_double = FALSE,
    trim_ws = TRUE
  ) %>%
  mutate(wave = as.integer(wave))

# create combined statements df
statements_raw <-
  list(statements_slant, statements_satire) %>%
  reduce(full_join, by = c("statement", "wave"))

statements_raw

```



# Participants

## Demographics

```{r demographics}
demos <- raw %>%
  select(id,
         birthyr,
         gender,
         educ) %>%
  replace_with_na(replace = list(
    birthyr = c(8, 9),
    gender = c(8, 9),
    educ = c(8, 9)
  )) %>%
  mutate(age = 2019 - birthyr) %>%
  mutate(gender = ifelse(gender == 1, "female", "male")) %>%
  mutate(gender = factor(gender, c("female", "male"))) %>%
  select(id,
         age,
         gender,
         educ)

# assert data properties
demos %>%
  assert(in_set(18:99), age) %>%
  assert(in_set(1:6), educ) %>%
  assert(not_na, everything())

```

## Political views

```{r political_views}
# replace values of 8 (participant did not answer) and 9 (statement was not shown to participant in block or participant did not participate in wave) with NA
political_views <- raw %>%
  select(id,
         pid3,
         polid_W1,
         ecoid_W1,
         socid_W1) %>%
  replace_with_na(replace = list(
    polid_W1 = c(8, 9),
    ecoid_W1 = c(8, 9),
    socid_W1 = c(8, 9),
    pid3 = c(8, 9)
  )) %>%
  mutate(pid3 = ordered(
    pid3,
    c(1, 2, 3, 4, 5),
    c("Democrat",
      "Republican",
      "Independent",
      "Other",
      "Not sure")
  ))

# assert data properties before averaging
political_views %>%
  assert(in_set(1:7), polid_W1, ecoid_W1, socid_W1) %>%
  assert(not_na, everything(), error_fun = just_warn)

# create df
political_views <- political_views %>%
  as_tibble %>%
  rowwise %>%
  mutate(ideology_index = mean(c(polid_W1, ecoid_W1, socid_W1), na.rm = TRUE)) %>%
  ungroup %>%
  mutate(ideology_index_rounded = round(ideology_index, digit = 0)) %>%
  mutate(ideology = ordered(
    ideology_index_rounded,
    c(1, 2, 3, 4, 5, 6, 7),
    c(
      "liberal",
      "liberal",
      "liberal",
      "moderate",
      "conservative",
      "conservative",
      "conservative"
    )
  )) %>%
  select(id,
         party = pid3,
         ideology_index,
         ideology_index_rounded,
         ideology) %>%
  filter(!is.na(ideology_index_rounded))

political_views

```

## Psychological factors

```{r psychological_factors}
# replace values of 8 (participant did not answer) and 9 (statement was not shown to participant in block or participant did not participate in wave) with NA
psychological_factors <- raw %>%
  select(
    id,
    Feel1_W1,
    Feel2_W1,
    Feel3_W1,
    Feel4_W1,
    Evid1_W1,
    Evid2_W1,
    Evid3_W1,
    Evid4_W1,
    TIP1_W1,
    TIP2_W1,
    TIP3_W1,
    TIP4_W1
  ) %>%
  replace_with_na(
    replace = list(
      Feel1_W1 = c(8, 9),
      Feel2_W1 = c(8, 9),
      Feel3_W1 = c(8, 9),
      Feel4_W1 = c(8, 9),
      Evid1_W1 = c(8, 9),
      Evid2_W1 = c(8, 9),
      Evid3_W1 = c(8, 9),
      Evid4_W1 = c(8, 9),
      TIP1_W1 = c(8, 9),
      TIP2_W1 = c(8, 9),
      TIP3_W1 = c(8, 9),
      TIP4_W1 = c(8, 9)
    )
  )

# assert data properties before averaging
psychological_factors %>%
  assert(
    in_set(1:5),
    Feel1_W1,
    Feel2_W1,
    Feel3_W1,
    Feel4_W1,
    Evid1_W1,
    Evid2_W1,
    Evid3_W1,
    Evid4_W1,
    TIP1_W1,
    TIP2_W1,
    TIP3_W1,
    TIP4_W1
  ) %>%
  assert(not_na, everything(), error_fun = just_warn)

# create df
psychological_factors <- psychological_factors %>%
  as_tibble %>%
  rowwise %>%
  mutate(faith_intuition = mean(c(Feel1_W1, Feel2_W1, Feel3_W1, Feel4_W1), na.rm = TRUE)) %>%
  mutate(need_evidence = mean(c(Evid1_W1, Evid2_W1, Evid3_W1, Evid4_W1), na.rm = TRUE)) %>%
  mutate(truth_political = mean(c(TIP1_W1, TIP2_W1, TIP3_W1, TIP4_W1), na.rm = TRUE)) %>%
  ungroup %>%
  select(id,
         faith_intuition,
         need_evidence,
         truth_political) %>%
  filter(!is.na(faith_intuition)) %>% 
  filter(!is.na(need_evidence)) %>% 
  filter(!is.na(truth_political))

psychological_factors

```

## Combine participant data

```{r participants}
participants <-
  list(demos, psychological_factors) %>%
  reduce(inner_join, by = "id")

participants <- participants %>%
  list(political_views) %>%
  reduce(inner_join, by = "id")

participants %>%
  assert(not_na, everything(), error_fun = just_warn)

participants

```



# Misinformation detection task

## Rating

```{r rating}
# e = recognition, b = truth judgment for familiar statements, bn = truth judgment for unfamiliar statements
# replace values of 8 (participant did not answer) and 9 (statement was not shown to participant in block or participant did not participate in wave) with NA
rating <- raw %>%
  select(id,
         contains("b_W"),
         contains("bn_W")) %>%
  pivot_longer(-id, names_to = "statement", values_to = "rating") %>%
  separate(statement, c("statement", "wave"), "_W") %>%
  type_convert %>%
  arrange(id, wave, statement) %>%
  separate(statement, c("statement", "block"), "b") %>%
  filter(rating != 8) %>%
  filter(rating != 9) %>%
  mutate(recog = ifelse(block == "n", 0, 1)) %>%
  mutate(truth = case_when(startsWith(statement, "T") ~ 1,
                           startsWith(statement, "F") ~ 0)) %>%
  select(-block) %>%
  mutate(statement = glue("w{wave}_{statement}")) %>%
  replace_with_na(replace = list(rating = 8)) %>%
  type_convert

# number of completed waves per participant
n_waves <- rating %>%
  group_by(id, wave) %>%
  summarize(n_items = n()) %>%
  group_by(id) %>%
  summarize(n_waves = n())

n_waves %>%
  assert(in_set(1:12), n_waves)

# number of responses per participant
n_statements <- rating %>% 
  group_by(id) %>% 
  summarize(n_statements = n())

n_statements %>%
  assert(in_set(0:240), n_statements)

# assert that there are exactly 20 statements for each participant per wave, but just warn as participants were allowed to skip statements
n_statements_wave <- rating %>%
  group_by(id, wave) %>%
  summarize(n_statements_wave = n()) %>%
  ungroup()

n_statements_wave %>%
  assert(in_set(20), n_statements_wave, error_fun = just_warn)

# assert data properties
rating %>%
  assert(in_set(1:12), wave) %>%
  assert(in_set(1:4), rating) %>%
  assert(in_set(0:1), recog) %>%
  assert(in_set(0:1), truth) %>%
  assert(not_na, id, statement, wave, truth) %>%
  assert(not_na, everything(), error_fun = just_warn)

```

## Decision

```{r decision}
# rating: 1 and 2 = 'true', 3 and 4 = 'false'
dec <- rating %>%
  select(-recog) %>%
  mutate(dec = as.integer(ifelse(rating == 1 |
                                   rating == 2, 1, 0))) %>%
  mutate(dec_correct = as.integer(ifelse(dec == truth, 1, 0))) %>%
  type_convert

# assert data properties
dec %>%
  assert(in_set(1:12), wave) %>%
  assert(in_set(1:4), rating) %>%
  assert(in_set(0:1), truth) %>%
  assert(in_set(0:1), dec) %>%
  assert(in_set(0:1), dec_correct) %>%
  assert(not_na, id, statement, wave, truth) %>%
  assert(not_na, everything(), error_fun = just_warn)

```

## Confidence

```{r confidence}
# rating: 1 and 4 = 'high confidence', 2 and 3 = 'low confidence'
conf <- rating %>%
  select(-recog,-truth) %>%
  mutate(conf_high = as.integer(ifelse(rating == 1 |
                                         rating == 4, 1, 0))) %>%
  select(-rating) %>%
  type_convert

# assert data properties
conf %>%
  assert(in_set(1:12), wave) %>%
  assert(in_set(0:1), conf_high) %>%
  assert(not_na, id, statement, wave) %>%
  assert(not_na, everything(), error_fun = just_warn)

```

## Recognition

```{r recognition}
recog <- raw %>%
  select(id,
         contains("e_W"),-c(contains("time"))) %>%
  pivot_longer(-id, names_to = "statement", values_to = "recog") %>%
  separate(statement, c("statement", "wave"), "e_W")

# assert data properties before recoding 'recog' variable
recog %>%
  assert(in_set(1:12), wave) %>%
  assert(in_set(1:2), recog) %>%
  assert(not_na, id, statement, wave) %>%
  assert(not_na, everything(), error_fun = just_warn)

# recode 'recog' variable
recog <- recog %>%
  mutate(recog = as.integer(ifelse(recog == 1, 1, 0))) %>%
  mutate (statement = glue("w{wave}_{statement}")) %>%
  filter(!is.na(recog)) %>%
  type_convert

# assert data properties
recog %>%
  assert(in_set(1:12), wave) %>%
  assert(in_set(0:1), recog) %>%
  assert(not_na, id, statement, wave) %>%
  assert(not_na, everything())

# assert same 'recog' responses for 'rating' and 'recog' dfs
overlap <- list(rating, recog) %>%
  reduce(full_join, by = c("id", "statement", "wave")) %>%
  select(-rating, -truth) %>%
  mutate(overlap = as.integer(ifelse(recog.x == recog.y, 1, 0)))

overlap %>%
  assert(in_set(1), overlap)

recog

```

## Statement slant and satire

```{r statements_slant_and_satire}
# recode statement slant data from 1/2/3 (pro-Democrat/pro-Republican/neutral) to 1/-1/0
statements <- statements_raw %>%
  mutate(rFavor = as.integer(ifelse(rFavor == 1, rFavor, rFavor - 3))) %>%
  mutate(dFavor = as.integer(ifelse(dFavor == 1, dFavor, dFavor - 3))) %>%
  mutate(pFavor = as.integer(ifelse(pFavor == 1, pFavor, pFavor - 3))) %>%
  mutate(statement = glue("w{wave}_{statement}"))

# assert data properties
statements %>%
  assert(in_set(1:12), wave) %>%
  assert(in_set(-1:1), rFavor) %>%
  assert(in_set(-1:1), dFavor) %>%
  assert(in_set(-1:1), pFavor) %>%
  assert(in_set(0:1), satire) %>%
  assert(not_na, everything())

statements

```

## Statement congruency

```{r statement_congruency}
# add political congruency of statements (1 = congruent; 2 = incongruent; 3 = neutral; 4 = neither congruent, incongruent, or neutral)
# `congruent_party` = statement congruency as a combination of a participant's political party and statement slant
# `congruent_ideology` = statement congruency as a combination of a participant's political ideology and statement slant
# `congruent_truth_party` = statement congruency as a combination of a participant's political party, statement slant, and statement veracity
# `congruent_truth_ideology` = statement congruency as a combination of a participant's political ideology, statement slant, and statement veracity
congruency <- dec %>%
  select(id, statement, wave, truth)

congruency <- congruency %>%
  list(statements) %>%
  reduce(left_join, by = c("statement", "wave"))

congruency <- congruency %>%
  list(participants) %>%
  reduce(right_join, by = c("id"))

congruency <- congruency %>%
  select(id, statement, wave, truth, pFavor, party, ideology) %>%
  mutate(
    congruent_party = case_when(
      party == "Democrat" &
        pFavor == "1" ~ 1,
      party == "Republican" &
        pFavor == "-1" ~ 1,
      party == "Democrat" &
        pFavor == "-1" ~ 2,
      party == "Republican" &
        pFavor == "1" ~ 2,
      party == "Democrat" &
        pFavor == "0" ~ 3,
      party == "Republican" &
        pFavor == "0" ~ 3,
      party == "Independent" &
        pFavor == "1" ~ 4,
      party == "Independent" &
        pFavor == "-1" ~ 4,
      party == "Independent" &
        pFavor == "0" ~ 4,
      party == "Other" &
        pFavor == "1" ~ 4,
      party == "Other" &
        pFavor == "-1" ~ 4,
      party == "Other" &
        pFavor == "0" ~ 4,
      party == "Not sure" &
        pFavor == "1" ~ 4,
      party == "Not sure" &
        pFavor == "-1" ~ 4,
      party == "Not sure" &
        pFavor == "0" ~ 4,
    )
  )  %>%
  mutate(
    congruent_ideology = case_when(
      ideology == "liberal" &
        pFavor == "1" ~ 1,
      ideology == "liberal" &
        pFavor == "-1" ~ 2,
      ideology == "liberal" &
        pFavor == "0" ~ 3,
      ideology == "moderate" &
        pFavor == "1" ~ 4,
      ideology == "moderate" &
        pFavor == "-1" ~ 4,
      ideology == "moderate" &
        pFavor == "0" ~ 4,
      ideology == "conservative" &
        pFavor == "1" ~ 2,
      ideology == "conservative" &
        pFavor == "-1" ~ 1,
      ideology == "conservative" &
        pFavor == "0" ~ 3,
    )
  )  %>%
  mutate(
    congruent_truth_party = as.numeric(case_when(
      party == "Democrat" & pFavor == 1 & truth == 1 ~ "1",
      party == "Democrat" & pFavor == 1 & truth == 0 ~ "2",
      party == "Democrat" & pFavor == -1 & truth == 1 ~ "2",
      party == "Democrat" & pFavor == -1 & truth == 0 ~ "1",
      party == "Democrat" & pFavor == 0 & truth == 1 ~ "3",
      party == "Democrat" & pFavor == 0 & truth == 0 ~ "3",
      party == "Republican" & pFavor == 1 & truth == 1 ~ "2",
      party == "Republican" & pFavor == 1 & truth == 0 ~ "1",
      party == "Republican" & pFavor == -1 & truth == 1 ~ "1",
      party == "Republican" & pFavor == -1 & truth == 0 ~ "2",
      party == "Republican" & pFavor == 0 & truth == 1 ~ "3",
      party == "Republican" & pFavor == 0 & truth == 0 ~ "3",
      party == "Independent" ~ "4",
      party == "Other" ~ "4",
      party == "Not sure" ~ "4",
    ))
  ) %>%
  mutate(
    congruent_truth_ideology = as.numeric(case_when(
      ideology == "liberal" & pFavor == 1 & truth == 1 ~ "1",
      ideology == "liberal" & pFavor == 1 & truth == 0 ~ "2",
      ideology == "liberal" & pFavor == -1 & truth == 1 ~ "2",
      ideology == "liberal" & pFavor == -1 & truth == 0 ~ "1",
      ideology == "liberal" & pFavor == 0 & truth == 1 ~ "3",
      ideology == "liberal" & pFavor == 0 & truth == 0 ~ "3",
      ideology == "conservative" & pFavor == 1 & truth == 1 ~ "2",
      ideology == "conservative" & pFavor == 1 & truth == 0 ~ "1",
      ideology == "conservative" & pFavor == -1 & truth == 1 ~ "1",
      ideology == "conservative" & pFavor == -1 & truth == 0 ~ "2",
      ideology == "conservative" & pFavor == 0 & truth == 1 ~ "3",
      ideology == "conservative" & pFavor == 0 & truth == 0 ~ "3",
      ideology == "moderate" ~ "4",
    ))
  ) %>%
  select(-pFavor, -truth, -party, -ideology)

# assert data properties
congruency %>%
  assert(in_set(1:4), congruent_party) %>%
  assert(in_set(1:4), congruent_ideology) %>%
  assert(in_set(1:4), congruent_truth_party) %>%
  assert(in_set(1:4), congruent_truth_ideology) %>%  
  assert(not_na, everything())

```


## Combine task data

```{r combined}
task <- list(dec, conf, recog) %>%
  reduce(full_join, by = c("id", "statement", "wave"))

task <- list(task, n_waves) %>%
  reduce(full_join, by = c("id"))

task <- list(task, n_statements) %>%
  reduce(full_join, by = c("id"))

task <- list(task, statements) %>% 
  reduce(left_join, by = c("statement", "wave")) %>% 
  select(-rFavor, -dFavor, -veracity, -statements, -url)

task <- list(task, congruency) %>% 
  reduce(full_join, by = c("id", "statement", "wave"))

# add dummy variable for `trials2counts.Rmd`
task <- task %>% 
  mutate(dummy = 1)

# assert data properties
task %>%
  assert(not_na, everything(), error_fun = just_warn)

task <- task %>%
  filter(!is.na(rating)) %>%
  filter(!is.na(congruent_party))

task %>%
  assert(not_na, everything())

```



# Satisficing

We seek to exclude participants who are strongly satisficing in their study
participation. Thus, we exclude participants' wave-level data for waves in which
they chose one of the four response options more than 90% of the time (following
Rollwage et al., 2018; https://doi.org/10.1016/j.cub.2018.10.053). 

```{r detecting_satisficing}
# identify id's and waves for which participants selected one response option more than 90% of the time
participants_satisficing <- task %>%
  group_by(id, wave, rating) %>%
  summarize(n_rating_selected = n()) %>%
  full_join(task %>%
              group_by(id, wave) %>%
              summarize(n_statements_wave = n()),
            by = c("id", "wave")) %>%
  mutate(perc_same_rating = n_rating_selected / n_statements_wave) %>%
  filter(perc_same_rating > .9) %>%
  ungroup

# assert data properties
participants_satisficing %>%
  assert(in_set(1:20), n_rating_selected, n_statements_wave) %>%
  assert(within_bounds(.9, 1, include.lower = FALSE, include.upper = TRUE),
         perc_same_rating) %>%
  assert(not_na, everything(), error_fun = just_warn)

# count participants satisficing
n_participants_satisficing <- participants_satisficing %>%
  distinct(id) %>%
  n_distinct()

perc_participants_satisficing <-
  (n_participants_satisficing / raw_n_initial) * 100

# count wave-id combinations to exclude
n_waves_excluded <- nrow(participants_satisficing)

perc_waves_excluded <-
  (n_waves_excluded / nrow(n_statements_wave)) * 100

```

Exclude wave-level data from `task` df for waves in which participants satisficed
and id's from `participants` df for id's which satisficed in all waves in which
they participated.

```{r exclude_satisficing_data}
# exclude wave-level data for satisficing participants from the `task` df
task <- task %>%
  anti_join(participants_satisficing, by = c("id", "wave"))

# remove id's who satisficed in all waves in which they participated from the `participants` df
participants_excluded <- participants_satisficing %>%
  count(id, name = "n_waves_satisficed") %>%
  inner_join(n_waves, by = "id") %>%
  mutate(perc_waves_satisficed = n_waves_satisficed / n_waves) %>%
  filter(perc_waves_satisficed == 1)

n_participants_excluded <- nrow(participants_excluded)

perc_participants_excluded <-
  (n_participants_excluded / raw_n_initial) * 100

participants <- participants %>%
  anti_join(participants_excluded, by = "id")

n_participants_final <- nrow(participants)

```

Based on our criterion for detecting satisficing, we exclude wave-level data from
`r n_participants_satisficing` participants (`r perc_participants_satisficing`%).
Specifically, we excluded `r n_waves_excluded` wave-id combinations (`r perc_waves_excluded`%).
This led to `r n_participants_excluded` participants (`r perc_participants_excluded`%)
being entirely excluded from the data, yielding a sample size of `r n_participants_final`
participants for model fitting using a hierarchical Bayesian approach (Fleming, 2017).



# Check overlap ids in `participants` and `task` dfs

```{r overlap}
# participants need to appear in both data frames
expect_equal(nrow(anti_join(participants, task)), 0)
expect_equal(nrow(anti_join(task, participants)), 0)

```



# Write to disk

```{r write_to_disk}
write_rds(raw, here("output/raw.rds"), compress = "gz")
write_csv(raw, here("output/raw.csv"))

write_rds(statements, here("output/statements.rds"), compress = "gz")
write_csv(statements, here("output/statements.csv"))

write_rds(task, here("output/task.rds"), compress = "gz")
write_csv(task, here("output/task.csv"))

write_rds(participants, here("output/participants.rds"), compress = "gz")
write_csv(participants, here("output/participants.csv"))

```
