---
title: "Robustness checks"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 3
editor_options:
  chunk_output_type: console
---



# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = TRUE,
	cache = FALSE
)

```



# Source `dependencies.R`

```{r dependencies, message=FALSE, code=readr::read_lines(here::here("code/_dependencies.R"))}
source(here::here("code/_dependencies.R"))

```



# Load data

```{r load_data}
# load dat
dat <- read_rds(here::here("output/dat.rds"))

# group-level model
metad_group <- read_rds(here::here("output/models/group/metad_group.rds"))

# individual-level mratio cleaned models
metad_indiv_all_participants_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_all_participants_m_ratio_cleaned.rds"))
metad_indiv_six_or_more_waves_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_six_or_more_waves_m_ratio_cleaned.rds"))
metad_indiv_twelve_waves_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_twelve_waves_m_ratio_cleaned.rds"))
metad_indiv_congruent_party_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_congruent_party_statements_m_ratio_cleaned.rds"))
metad_indiv_incongruent_party_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_incongruent_party_statements_m_ratio_cleaned.rds"))
metad_indiv_neutral_party_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_neutral_party_statements_m_ratio_cleaned.rds"))
metad_indiv_congruent_ideology_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_congruent_ideology_statements_m_ratio_cleaned.rds"))
metad_indiv_incongruent_ideology_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_incongruent_ideology_statements_m_ratio_cleaned.rds"))
metad_indiv_neutral_ideology_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_neutral_ideology_statements_m_ratio_cleaned.rds"))
metad_indiv_congruent_truth_party_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_congruent_truth_party_statements_m_ratio_cleaned.rds"))
metad_indiv_incongruent_truth_party_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_incongruent_truth_party_statements_m_ratio_cleaned.rds"))
metad_indiv_neutral_truth_party_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_neutral_truth_party_statements_m_ratio_cleaned.rds"))
metad_indiv_congruent_truth_ideology_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_congruent_truth_ideology_statements_m_ratio_cleaned.rds"))
metad_indiv_incongruent_truth_ideology_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_incongruent_truth_ideology_statements_m_ratio_cleaned.rds"))
metad_indiv_neutral_truth_ideology_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_neutral_truth_ideology_statements_m_ratio_cleaned.rds"))
metad_indiv_recognized_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_recognized_statements_m_ratio_cleaned.rds"))
metad_indiv_non_recognized_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_non_recognized_statements_m_ratio_cleaned.rds"))
metad_indiv_satire_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_satire_statements_m_ratio_cleaned.rds"))
metad_indiv_non_satire_statements_m_ratio_cleaned <- read_rds(here::here("output/models/indiv/mratio_cleaned/metad_indiv_non_satire_statements_m_ratio_cleaned.rds"))

# individual-level Mdiff cleaned models
metad_indiv_all_participants_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_all_participants_m_diff_cleaned.rds"))
metad_indiv_six_or_more_waves_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_six_or_more_waves_m_diff_cleaned.rds"))
metad_indiv_twelve_waves_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_twelve_waves_m_diff_cleaned.rds"))
metad_indiv_congruent_party_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_congruent_party_statements_m_diff_cleaned.rds"))
metad_indiv_incongruent_party_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_incongruent_party_statements_m_diff_cleaned.rds"))
metad_indiv_neutral_party_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_neutral_party_statements_m_diff_cleaned.rds"))
metad_indiv_congruent_ideology_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_congruent_ideology_statements_m_diff_cleaned.rds"))
metad_indiv_incongruent_ideology_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_incongruent_ideology_statements_m_diff_cleaned.rds"))
metad_indiv_neutral_ideology_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_neutral_ideology_statements_m_diff_cleaned.rds"))
metad_indiv_congruent_truth_party_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_congruent_truth_party_statements_m_diff_cleaned.rds"))
metad_indiv_incongruent_truth_party_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_incongruent_truth_party_statements_m_diff_cleaned.rds"))
metad_indiv_neutral_truth_party_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_neutral_truth_party_statements_m_diff_cleaned.rds"))
metad_indiv_congruent_truth_ideology_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_congruent_truth_ideology_statements_m_diff_cleaned.rds"))
metad_indiv_incongruent_truth_ideology_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_incongruent_truth_ideology_statements_m_diff_cleaned.rds"))
metad_indiv_neutral_truth_ideology_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_neutral_truth_ideology_statements_m_diff_cleaned.rds"))
metad_indiv_recognized_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_recognized_statements_m_diff_cleaned.rds"))
metad_indiv_non_recognized_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_non_recognized_statements_m_diff_cleaned.rds"))
metad_indiv_satire_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_satire_statements_m_diff_cleaned.rds"))
metad_indiv_non_satire_statements_m_diff_cleaned <- read_rds(here::here("output/models/indiv/mdiff_cleaned/metad_indiv_non_satire_statements_m_diff_cleaned.rds"))

```



# Group-level models

```{r group_models}
# create df for all participants
df_all_participants <- metad_group %>%
  filter(group %in% "all") %>%
  mutate(items = factor(
    items,
    levels = c(
      "all",
      "recognized",
      "unrecognized",
      "satire",
      "non-satire",
      "congruent_truth_party",
      "incongruent_truth_party",
      "neutral_truth_party",
      "congruent_party",
      "incongruent_party",
      "neutral_party",
      "congruent_truth_ideology",
      "incongruent_truth_ideology",
      "neutral_truth_ideology",
      "congruent_ideology",
      "incongruent_ideology",
      "neutral_ideology"
    )
  ))

# plot d1
fig_all_participants_d1 <- df_all_participants %>%
  ggplot(aes(
    x = items,
    y = d1_g,
    ymin = d1_g.lower,
    ymax = d1_g.upper
  )) +
  scale_y_continuous(breaks = pretty_breaks(10)) +
  coord_fixed(ratio = 2) +
  ylim(0, max(df_all_participants$Mratio_g.upper)) +
  geom_pointrange() +
  labs(x = "", y = "d'") +
  theme_minimal_hgrid() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
fig_all_participants_d1

# plot meta-d'
fig_all_participants_meta_d1 <- df_all_participants %>%
  ggplot(aes(
    x = items,
    y = meta_d1_g,
    ymin = meta_d1_g.lower,
    ymax = meta_d1_g.upper
  )) +
  scale_y_continuous(breaks = pretty_breaks(10)) +
  coord_fixed(ratio = 2) +
  ylim(0, max(df_all_participants$Mratio_g.upper)) +
  geom_pointrange() +
  labs(x = "", y = "meta-d'") +
  theme_minimal_hgrid() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
fig_all_participants_meta_d1

# plot Mratio
fig_all_participants_mratio <- df_all_participants %>%
  ggplot(aes(
    x = items,
    y = Mratio_g,
    ymin = Mratio_g.lower,
    ymax = Mratio_g.upper
  )) +
  scale_y_continuous(breaks = pretty_breaks(10)) +
  coord_fixed(ratio = 2) +
  ylim(0, max(df_all_participants$Mratio_g.upper)) +
  geom_pointrange() +
  geom_hline(yintercept = 1, linetype = "dashed") +
  labs(x = "", y = "Mratio") +
  theme_minimal_hgrid() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
fig_all_participants_mratio

# plot M-diff
fig_all_participants_mdiff <- df_all_participants %>%
  ggplot(aes(
    x = items,
    y = Mdiff_g,
    ymin = Mdiff_g.lower,
    ymax = Mdiff_g.upper
  )) +
  scale_y_continuous(breaks = pretty_breaks(10)) +
  coord_fixed(ratio = 2) +
  ylim(min(df_all_participants$Mdiff_g.lower),
       max(df_all_participants$Mdiff_g.upper)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "", y = "M-diff") +
  theme_minimal_hgrid() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
fig_all_participants_mdiff

# merge and save plots
fig_all_participants_merged <- ggarrange(
  fig_all_participants_d1,
  fig_all_participants_meta_d1,
  fig_all_participants_mratio,
  ncol = 1,
  nrow = 3,
  labels = c("A", "B", "C"),
  common.legend = TRUE,
  legend = "right"
)
fig_all_participants_merged

save_plot(
  here("output/figures/fig_all_participants_merged.pdf"),
  fig_all_participants_merged,
  base_width = 10,
  base_height = 20
)

save_plot(
  here("output/figures/fig_all_participants_mdiff.pdf"),
  fig_all_participants_mdiff,
  base_width = 15,
  base_height = 3
)

```



# Individual-level models

## Mratio

### Participant attrition

```{r individual_m_ratio_participant_attrition}
df_combined <- bind_rows(
  metad_indiv_all_participants_m_ratio_cleaned %>% mutate(group = "All participants"),
  metad_indiv_six_or_more_waves_m_ratio_cleaned %>% mutate(group = "Six or more waves"),
  metad_indiv_twelve_waves_m_ratio_cleaned %>% mutate(group = "Twelve waves")
)

fig_robustness_m_ratio_indiv_participant_attrition <-
  ggplot(df_combined, aes(x = group, y = m_ratio)) +
  geom_boxplot() +
  geom_hline(yintercept = 1, linetype = "dashed") +
  labs(x = "", y = "Mratio") +
  theme_minimal_hgrid()
fig_robustness_m_ratio_indiv_participant_attrition

save_plot(
  here("output/figures/fig_SI_robustness_m_ratio_indiv_participant_attrition.pdf"),
  fig_robustness_m_ratio_indiv_participant_attrition,
  base_width = 8,
  base_height = 6
)

```



### Statement characteristics

Write function to compare Mratios for different statement subgroups

```{r function_indiv_m_ratio}
fnc_scatterplot <-
  function(df1,
           df2,
           x_axis_label = "m_ratio in df1",
           y_axis_label = "m_ratio in df2") {
    df_combined <-
      inner_join(select(df1, id, m_ratio), select(df2, id, m_ratio), by = "id")
    
    ggplot(df_combined, aes(x = m_ratio.x, y = m_ratio.y)) +
      geom_abline(intercept = 0,
                  slope = 1,
                  linetype = "dashed")  +
      stat_smooth(
        method = "loess",
        method.args = list(family = "symmetric"),
        alpha = .15
      ) +
      geom_point(alpha = .5) +
      guides(color = guide_legend(reverse = TRUE),
             fill = guide_legend(reverse = TRUE)) +
      labs(x = x_axis_label, y = y_axis_label)
  }

```

Apply function

```{r}
# congruent vs. incongruent statements (party*truth)
fig_robustness_m_ratio_congruent_incongruent <- fnc_scatterplot(
  metad_indiv_congruent_truth_party_statements_m_ratio_cleaned,
  metad_indiv_incongruent_truth_party_statements_m_ratio_cleaned,
  x_axis_label = "Mratio for congruent statements (party*truth)",
  y_axis_label = "Mratio for incongruent statements (party*truth)"
)
fig_robustness_m_ratio_congruent_incongruent

# congruent vs. neutral statements (party*truth)
fig_robustness_m_ratio_congruent_neutral <- fnc_scatterplot(
  metad_indiv_congruent_truth_party_statements_m_ratio_cleaned,
  metad_indiv_neutral_truth_party_statements_m_ratio_cleaned,
  x_axis_label = "Mratio for congruent statements (party*truth)",
  y_axis_label = "Mratio for neutral statements (party*truth)"
)
fig_robustness_m_ratio_congruent_neutral

# incongruent vs. neutral statements (party*truth)
fig_robustness_m_ratio_incongruent_neutral <- fnc_scatterplot(
  metad_indiv_incongruent_truth_party_statements_m_ratio_cleaned,
  metad_indiv_neutral_truth_party_statements_m_ratio_cleaned,
  x_axis_label = "Mratio for incongruent statements (party*truth)",
  y_axis_label = "Mratio for neutral statements (party*truth)"
)
fig_robustness_m_ratio_incongruent_neutral

# recognized vs. unrecognized statements
fig_robustness_m_ratio_recognized_unrecognized <- fnc_scatterplot(
  metad_indiv_recognized_statements_m_ratio_cleaned,
  metad_indiv_non_recognized_statements_m_ratio_cleaned,
  x_axis_label = "Mratio for recognized statements",
  y_axis_label = "Mratio for unrecognized statements"
)
fig_robustness_m_ratio_recognized_unrecognized

# satire vs. non-satire statements
fig_robustness_m_ratio_satire_non_satire <- fnc_scatterplot(
  metad_indiv_satire_statements_m_ratio_cleaned,
  metad_indiv_non_satire_statements_m_ratio_cleaned,
  x_axis_label = "Mratio for satire statements",
  y_axis_label = "Mratio for non-satire statements"
)
fig_robustness_m_ratio_satire_non_satire

# all plots in one figure
fig_robustness_m_ratio_indiv_statement_characteristics <- ggarrange(
  fig_robustness_m_ratio_congruent_incongruent,
  fig_robustness_m_ratio_congruent_neutral,
  fig_robustness_m_ratio_incongruent_neutral,
  fig_robustness_m_ratio_recognized_unrecognized,
  fig_robustness_m_ratio_satire_non_satire,
  ncol = 3,
  nrow = 2,
  labels = c("A", "B", "C", "D", "E")
)
fig_robustness_m_ratio_indiv_statement_characteristics

save_plot(
  here("output/figures/fig_robustness_m_ratio_indiv_statement_characteristics.pdf"),
  fig_robustness_m_ratio_indiv_statement_characteristics,
  base_width = 16,
  base_height = 12
)

```



## Mdiff

### Participant attrition

```{r individual_m_diff_participant_attrition}
df_combined <- bind_rows(
  metad_indiv_all_participants_m_diff_cleaned %>% mutate(group = "All participants"),
  metad_indiv_six_or_more_waves_m_diff_cleaned %>% mutate(group = "Six or more waves"),
  metad_indiv_twelve_waves_m_diff_cleaned %>% mutate(group = "Twelve waves")
)

fig_robustness_m_diff_indiv_attrition <-
  ggplot(df_combined, aes(x = group, y = m_diff)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "", y = "Mdiff") +
  theme_minimal_hgrid()
fig_robustness_m_diff_indiv_attrition

save_plot(
  here("output/figures/fig_robustness_m_diff_indiv_attrition.pdf"),
  fig_robustness_m_diff_indiv_attrition,
  base_width = 8,
  base_height = 6
)

```

### Statement characteristics

Write function to compare Mdiffs for different statement subgroups

```{r function_indiv_m_diff}
fnc_scatterplot <-
  function(df1,
           df2,
           x_axis_label = "m_diff in df1",
           y_axis_label = "m_diff in df2") {
    df_combined <-
      inner_join(select(df1, id, m_diff), select(df2, id, m_diff), by = "id")
    
    ggplot(df_combined, aes(x = m_diff.x, y = m_diff.y)) +
      geom_abline(intercept = 0,
                  slope = 1,
                  linetype = "dashed")  +
      stat_smooth(
        method = "loess",
        method.args = list(family = "symmetric"),
        alpha = .15
      ) +
      geom_point(alpha = .5) +
      guides(color = guide_legend(reverse = TRUE),
             fill = guide_legend(reverse = TRUE)) +
      labs(x = x_axis_label, y = y_axis_label)
  }

```

Apply function

```{r}
# congruent vs. incongruent statements (party*truth)
fig_robustness_m_diff_congruent_incongruent <- fnc_scatterplot(
  metad_indiv_congruent_truth_party_statements_m_diff_cleaned,
  metad_indiv_incongruent_truth_party_statements_m_diff_cleaned,
  x_axis_label = "Mdiff for congruent statements (party*truth)",
  y_axis_label = "Mdiff for incongruent statements (party*truth)"
)
fig_robustness_m_diff_congruent_incongruent

# congruent vs. neutral statements (party*truth)
fig_robustness_m_diff_congruent_neutral <- fnc_scatterplot(
  metad_indiv_congruent_truth_party_statements_m_diff_cleaned,
  metad_indiv_neutral_truth_party_statements_m_diff_cleaned,
  x_axis_label = "Mdiff for congruent statements (party*truth)",
  y_axis_label = "Mdiff for neutral statements (party*truth)"
)
fig_robustness_m_diff_congruent_neutral

# incongruent vs. neutral statements (party*truth)
fig_robustness_m_diff_incongruent_neutral <- fnc_scatterplot(
  metad_indiv_incongruent_truth_party_statements_m_diff_cleaned,
  metad_indiv_neutral_truth_party_statements_m_diff_cleaned,
  x_axis_label = "Mdiff for incongruent statements (party*truth)",
  y_axis_label = "Mdiff for neutral statements (party*truth)"
)
fig_robustness_m_diff_incongruent_neutral

# recognized vs. unrecognized statements
fig_robustness_m_diff_recognized_unrecognized <- fnc_scatterplot(
  metad_indiv_recognized_statements_m_diff_cleaned,
  metad_indiv_non_recognized_statements_m_diff_cleaned,
  x_axis_label = "Mdiff for recognized statements",
  y_axis_label = "Mdiff for unrecognized statements"
)
fig_robustness_m_diff_recognized_unrecognized

# satire vs. non-satire statements
fig_robustness_m_diff_satire_non_satire <- fnc_scatterplot(
  metad_indiv_satire_statements_m_diff_cleaned,
  metad_indiv_non_satire_statements_m_diff_cleaned,
  x_axis_label = "Mdiff for satire statements",
  y_axis_label = "Mdiff for non-satire statements"
)
fig_robustness_m_diff_satire_non_satire

# all plots in one figure
fig_robustness_m_diff_indiv_statement_characteristics <- ggarrange(
  fig_robustness_m_diff_congruent_incongruent,
  fig_robustness_m_diff_congruent_neutral,
  fig_robustness_m_diff_incongruent_neutral,
  fig_robustness_m_diff_recognized_unrecognized,
  fig_robustness_m_diff_satire_non_satire,
  ncol = 3,
  nrow = 2,
  labels = c("A", "B", "C", "D", "E")
)
fig_robustness_m_diff_indiv_statement_characteristics

save_plot(
  here("output/figures/fig_robustness_m_diff_indiv_statement_characteristics.pdf"),
  fig_robustness_m_diff_indiv_statement_characteristics,
  base_width = 16,
  base_height = 12
)

```
